Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-29 paper-ieee-trans.tex
Minor fix in caption text for Fig3
Minor addition

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{images/fig3.png}
\caption{Adoption of Configuration Management tools throughout the project lifetime. Also shown the trend lines
leading to the first release (light cream points and line), and to the second release (dark blue points and line).}
\label{fig:fig_confman}
\end{figure}

@@

Fig.~\ref{fig:fig_jenkins_CI_builds} shows the evolution, throughout the
{\sl INDIGO--DataCloud}'s first and second releases, of the required test types builds since the
implementation of the CI infrastructure. Automated functional testing coverage were not
available for all the software stack, thus the associated number of builds are fewer. Towards the
end of the project, the software development activity slowed the pace but not completely ceased
as the CI infrastructure is still maintained after the project's end of life.

>>>>

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{images/fig3.png}
\caption{Adoption of Configuration Management tools throughout the project lifetime. The figure shows the trend lines
leading to the first (light cream points and line) and second release (dark blue points and line).}
\label{fig:fig_confman}
\end{figure}

@@

Fig.~\ref{fig:fig_jenkins_CI_builds} shows the evolution, throughout the
{\sl INDIGO--DataCloud}'s first and second releases, of the required test types builds since the
implementation of the CI infrastructure. Automated functional testing coverage were not
available for all the software stack, thus the associated number of builds are fewer. Towards the
end of the project, the software development activity slowed the pace but not completely ceased
as the CI infrastructure is still maintained and used after the project's end of life.
